Application of Huynh 2020 Interim Analysis methods to assessed stocks from the US South Atlantic

### 2022-06-02 RunMSE/SEFSC/MSEPlots.Rmd
move large files out of repo

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10)

library(Hmisc)
library(knitr)
library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
library(SAMtool)
library(stringr)
library(bamExtras)

@@

# Median without NA
median_noNA <- function(x){median(x,na.rm=TRUE)}
```

```{r user}
# Should individual PDFs be produced (or just plot in Rmd output)
plot_pdf <- TRUE

OMNames_user <- c("OM_BlackSeaBass",
                  "OM_VermilionSnapper",
                  "OM_RedPorgy",
                   #"OM_Tilefish","OM_Cobia",
                  "OM_SnowyGrouper"#,
                  #"OM_GagGrouper")#,
                   #"OM_capelin", "OM_POP", "OM_vs"
                   )
OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")

scenNames_user1 <-  c("base","dep","lf","epiM","ubias","tachi","rc")
scenNames_user2 <-  c("base","nolag","minerr","minrecdev","perfobs","ucvhi","ucvlo","vtiv"
                        )

# All scenarios
scenNames_user <- unique(c(scenNames_user1,scenNames_user2))

# Alternative realities
# These scenarios are considered equally plausible, for the purposes of
# averaging results together. Most other scenarios could be considered sensitivities.
scenNames_user_alt <- c("base","dep","lf","epiM","ubias","tachi","rc")

scenNames_key <- c("base"="Base",
                   "nolag"="No data lag",
                   "hs"="Hyper-stable","hd"="Hyper-deplete",
                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "perfobs"="Perfect observation",
                   "minerr"="Minimal error",
                   "minrecdev"="Minimal rec devs",
                   "tachi"="TAC 1.25MSY",
                   "vtiv"="V time invariant"
                   )

MPNamesAll <-         c(#"AvC",
                        "CC1",
                        #"DCAC","DBSRA","SPMSY",
                        "SCA_1","SCA_5","SCA_10",
                        "iMP_avg_5","iMP_avg_10",
                        "iMP_buffer_5","iMP_buffer_10",
                        "pMP_5","pMP_10"
                        )

MPNamesAll_key <- c("AvC"="average catch",
                    "CC1"="average catch (last 5 yr)",
                    "DCAC"= "depletion corrected average catch",
                    "DBSRA" = "depletion based stock reduction analysis",
                    "SPMSY" = "surplus production model",
                    "SCA_1" = "SCA 1 yr",
                    "SCA_5" = "SCA 5 yr",
                    "SCA_10"= "SCA 10 yr",
                    "iMP_avg_5" = "avg. index (5 yr)",
                    "iMP_avg_10" = "avg. index (10 yr)",
                    "iMP_buffer_5" = "buffer index (5 yr)",
                    "iMP_buffer_10" = "buffer index (10 yr)",
                    "pMP_5" = "projection (5 yr)",
                    "pMP_10" = "projection (10 yr)"
                        )
MPNamesAll_legtext <- MPNamesAll

MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
                     )
MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
                             )

# OMNames_user <- c("OM_BlackSeaBass","OM_SnowyGrouper","OM_VermilionSnapper")
# OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
```

@@

```{r functions}
# color function like rainbow() but without yellow (or indigo)
ROGBP <- colorRampPalette(c("red","orange","green","blue","purple"))
# Makes an ROGBP function with an alpha channel
ROGBP_alpha <- function(alpha){
  x <- colorRampPalette(c(
    rgb(1,0,0,alpha), # red
    rgb(1,0.5,0.25,alpha), # orange
    rgb(0,1,0,alpha), # green 
    rgb(0,0,1,alpha), # blue
    rgb(0.5,0,0.5,alpha)), # purple
    alpha=TRUE)
  return(x)
}

@@

@@

plot_MSE_ts <- function(
myvarName="SSB",
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean,
scenNames,
OMNames,
MPNamesSub = NULL,
MPNamesSub_legtext=MPNamesSub,
MPNamesRef = NULL, # Name of reference MP
FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
legtext_o = NULL, # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,
sims = NULL, # which simulation runs should be used to generate the plot when plot_type="sims"?
plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
                   # "tradeoff" plots tradeoff plots by MP
                   # "addind" plot additional indices from AddInd
                   # "sims" plot time series for individual sim runs
proyear_phase=NULL,
PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
PMy = P75, # Performance metric function y (y-axis) for tradeoff plots)
mar=c(1,1,1,1),
oma=c(6,4,3,3),
mgp=c(1.5,0.2,0),
cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
xlabel = "Management year",
main_line = 1, # Line for main column labels
xlim = NULL,
ylim = NULL,
assessmentYears=NULL,
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.5),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){
if(is.null(legtext_o)){
  legtext_o <- seq_along(MPNamesSub)
}

@@

if(plot_type=="addind"){
  mfcol <- c(dim2,dim1)}else{
  mfcol <- c(dim1,dim2)
}

par(mfcol=mfcol,mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="r",yaxs="r")

### LOOP THROUGH MSE OBJECTS
for(outName_i in MSEoutNames){
topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
bottomPanels <- length(scenNames)*seq_along(OMNames)
leftPanels <- seq_along(scenNames)
rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))

@@

matplot(projYears_i#as.numeric(rownames(myvarsubStat))
        ,myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)

grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty="1111",lwd=2)
}
    if(plot_type=="sims"){
      cols <-  ROGBP(length(sims))
      ltys <-  1:length(MPNamesSub)
      pchs <-  NA
      lwds <-  3
      types <- "l"

@@

      for(MP_j in MPNamesSub){
      j <- match(MP_j,MPNamesSub)
      myvarsub_j <- myvarsub[,j,]
      lty <- ltys[j]
      if(j==1){
      matplot(projYears_i,
              t(myvarsub_j), 
              col=cols,lty=lty,lwd=lwds,type=types,
              xaxt=xaxt_i,yaxt=yaxt_i,
              xlim=xlim,ylim=ylim,xlab="",ylab="")
      #title(main=colLabsAll[i],line=1)

      grid(nx=NA,ny=NULL)
      abline(v=assessmentYears,lty=2,lwd=1)
      }else{
        matpoints(t(myvarsub_j), 
                col=cols,lty=lty,lwd=lwds,type=types
                )        
      }
    }
    }

if(plot_type=="addind"){
  PPDYears_i <- local({
    a <- c(histYears,projYears_i)
    a[-length(a)]
  })
if(is.null(assessmentYears)){
assessmentYears <- apply(do.call(cbind,lapply(out_i@PPD[[MPNamesSub]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
}

@@

plot_boot_vec(myvarsub[,j,],
              col_lines = col_AddInd[j],
              add=ifelse(j!=1,TRUE,FALSE),
              xlim=xlim,ylim=ylim)

}
grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty=2,lwd=1)
}

@@

if(is.null(proyear_phase)){
  proyear_phase <- out_i@proyears
}
Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase]
Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase]

matplot(Fstatus,Bstatus,
        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlab="",ylab="",xlim=xlim,ylim=ylim
        )
points(apply(Fstatus,2,median),
       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))

@@

@@

if(i%in%rightPanels){
row.ct <- which(rightPanels==i)
rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2
text(x=par("usr")[2]+diff(par("usr")[1:2])*0.1
     ,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=2)
}

@@

if(i==legend_panel&plot_type%in%c("huynh","phase","tradeoff")){
   legend(legend_x,
          inset=legend_inset,
       horiz=TRUE,bty="n",
       legend=MPNamesSub_legtext[legtext_o],
       col=makeOpaque(cols)[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],pch=pchs[legtext_o],
       cex=legend_cex,
       xpd=NA,
       x.intersp=0.5
       )

@@

if(textlabpos[i]=="lo"){text(x=x,y=rep(par("usr")[3]),labels=Statmedtext,srt=90,adj=c(-0.1,0.5),font=2)}
if(textlabpos[i]=="up"){text(x=x,y=rep(par("usr")[4]),labels=Statmedtext,srt=90,adj=c(1.2,0.5),font=2)}

@@

text(x=par("usr")[2]*1.05,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=2)
}

@@

```{r function PMsummary}
# compute and plot summary statistics for Performance metrics
PMsummary <- function(PMName,OMNames=OMNames_user,scenNames,MPs=NULL,
                      slot_to_plot="Prob", # Can be either "Prob" or "Stat"
                      main_line=-1.5,
                      hline=1,hline_lty=1,
                      par_args=list(mfrow=c(length(OMNames),1), 
                                    mar=c(0,2,0,1), oma=c(6,2,1,0),
                                    mgp=c(0.8,0.2,0), tck=-0.01),
                      ...){
PM <- get(PMName)
dots <- list(...)
if(!"ylab"%in%names(dots)){
  dots$ylab <- PMName
}

@@

for (OMNames_i in OMNames){
Names_i <- gsub("^OM_","",OMNames_i)
MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames_i))
                     )
    out_list_i <- list()
    for(MSEoutNames_ij in MSEoutNames_i){
      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
      MSEout_ij <- get(MSEoutNames_ij)
      PMout_ij <- PM(MSEout_ij)
        MPs_ij <- PMout_ij@MPs
        out_ij <- slot(PMout_ij,slot_to_plot)
      if(!is.null(MPs)){
        out_ij <- out_ij[,match(MPs,MPs_ij)]
        MPs_ij <- MPs
      }
      dimnames(out_ij) <- list("sim"=seq(1:dim(out_ij)[1]), "MPs"=MPs_ij)
      out_ij <- cbind("scen"=scenNames_j,as.data.frame(out_ij))
      out_list_i[[MSEoutNames_ij]] <- out_ij

    }
    # Combine scenario outputs into large data frame with scen column indicating scenario
      out_df_i <- do.call(rbind,out_list_i)
      out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i
    # Plot stuff
      dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"s","n")

      do.call(boxplot,c(list(out_df_i[,-1],main=""),dots))
      mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
      abline(h=hline,lty=hline_lty)
    }

@@

```{r data}
# Read in data for original operating models
for(file.i in list.files("OM")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM",file.i)))
}

# Read in data for modified operating models
for(file.i in list.files("OM_modified")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
}

@@

```{r plot sims base}
MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
scen <- "base"

>>>>

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.width=9,fig.height=11)

library(Hmisc)
library(knitr)
library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
library(openMSE)
library(stringr)
library(bamExtras)
library(bamMSE)
library(zoo)

@@

# Median without NA
median_noNA <- function(x){median(x,na.rm=TRUE)}

# ts_reldiff()
# Compute relative absolute differences in time series values
ts_reldiff <- function(x,denom_type="x2", # "rollmean" can also be used for the denominator for scaling the diffs
                       lag=1,type="absreldiff",
                       rollmean_args=list(k=11,fill="extend")
                       ){
  Yrs <- c(1,length(x))
  y1 <- Yrs[1]:(Yrs[2] - lag)
  y2 <- (Yrs[1] + lag):Yrs[2]
  x1 <- x[y1]
  x2 <- x[y2]
  rollmeanx2 <- do.call(rollmean,c(list(x=x),rollmean_args))[y2]

  diff <-   x1-x2
  denom <- switch(denom_type,
                  x2=x2,
                  rollmean=  rollmeanx2
                  )
  reldiff <- diff/denom
  absreldiff <- (reldiff^2)^0.5
  out <- switch(type,
                diff=diff,
                reldiff=reldiff,
                absreldiff=absreldiff
                )
  return(out)
}
```

```{r user}
# Should individual PDFs be produced (or just plot in Rmd output)
plot_pdf <- TRUE
generate_Hist <- FALSE
plot_Hist <- TRUE

boxplot_outline <- FALSE # Should outliers be plotted in boxplots?
boxplot_range <- 1.5 # Set range of whiskers in boxplots. A value of zero plots whiskers to data extremes.

OMNames_user <- c("OM_BlackSeaBass",
                  "OM_VermilionSnapper",
                  "OM_RedPorgy",
                   #"OM_Tilefish","OM_Cobia",
                  "OM_SnowyGrouper"#,
                  #"OM_GagGrouper"
                   )
Names_user <- gsub("^OM_","",OMNames_user)

OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")

# Sets of scenarios
sN1 <- "base"
sN2 <-  c("base","ucvhi","ucvlo","ubias","tachi","taclo")
sN3 <-  c("base","rc","minerr","minrecdev","recns","vtiv","vdome")
sN4 <-  c("base","noempind","catcvlo","nolag","perfobs","dep","lf")
sN5 <-  c("base","lhset","Mset","steepset","constM","epiM")

sN_all <- c("sN1","sN2","sN3","sN4","sN5")

# Run these sets
sN_run <- c("sN1"
            ,"sN2"
            #"sN3"
            #,"sN4"
            #,"sN5"
            )

# All scenarios
sN <- unique(as.character(unlist(sapply(sN_run,get))))

sN_plot <- sN_run

# Alternative realities
# These scenarios are considered equally plausible, for the purposes of
# averaging results together. Most other scenarios could be considered sensitivities.
# sN_alt <- sN1

scenNames_key <- c("base"="Base",
                   "catcvlo"="Catch CV 0.05",
                   "constM"="Constant M",
                   "dep"="More depleted",
                   "epiM"="Episodic M",
                   "hd"="Hyper-deplete",
                   "hs"="Hyper-stable",
                   "lf"="Less depleted",
                   "lhset"="Set M and steep",
                   "mconst"="M constant",
                   "minerr"="Minimal error",
                   "minrecac"="Minimal rec AC",
                   "minrecdev"="Minimal rec devs",
                   "Mset"="Set M",
                   "noempind"="No empirical indices",
                   "nolag"="No data lag",
                   "perfobs"="Perfect observation",
                   "rc"="Regime\nchange",
                   "recns"="Recruitment\nnonstationary",
                   "steepset"="Set steepness",
                   "tachi"="TAC 1.25MSY",
                   "taclo"="TAC 0.75MSY",
                   "ubias"="Index\nbiased",
                   "ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "vdome"="V dome-shaped",
                   "vtiv"="V time invariant"
                   )

MPNamesAll <-         c(#"AvC",
                        #"CC1", #"DCAC","DBSRA",
                        #"SPMSY",
                        "SCA_1","SCA_5","SCA_10",
                        "pMP_5","pMP_10",                        
                        "iMP_avg_5","iMP_avg_10",
                        "iMP_buffer_5","iMP_buffer_10"
                        )

MPNamesAll_key <- c("AvC"="average catch",
                    "CC1"="average catch (last 5 yr)",
                    "DCAC"= "depletion corrected average catch",
                    "DBSRA" = "depletion based stock reduction analysis",
                    "SPMSY" = "surplus production model",
                    "SCA_1" = "Annual SCA",
                    "SCA_5" = "Fixed TAC (5)",
                    "SCA_10"= "Fixed TAC (10)",
                    "iMP_avg_5" = "Avg Index (5)",
                    "iMP_avg_10" = "Avg Index (10)",
                    "iMP_buffer_5" = "Buffer Index (5)",
                    "iMP_buffer_10" = "Buffer Index (10)",
                    "pMP_5" = "Projection (5)",
                    "pMP_10" = "Projection (10)"
                        )
MPNamesAll_legtext <- MPNamesAll

MPNamesSub_userB <- c("SCA_1","SCA_5","pMP_5","iMP_avg_5","iMP_buffer_5")
MPNamesSub_userB_legtext <- MPNamesAll_key[MPNamesSub_userB]

MPNamesSub_userA <- c("SCA_1","SCA_10","pMP_10","iMP_avg_10","iMP_buffer_10")
MPNamesSub_userA_legtext <- MPNamesAll_key[MPNamesSub_userA]

MPNamesAll_abb <- local({
  a <- MPNamesAll
  a <- gsub("iMP_buffer","Bfr I",a)
  a <- gsub("iMP_avg","Avg I",a)
  a <- gsub("pMP","Proj",a)
  a <- gsub("iMP_","I",a)
  a <- gsub("_([0-9]+)$"," (\\1)",a)
  a
  #parse(text=a)
  })
```

@@

```{r functions}
# color function like rainbow() but without yellow (or indigo)
blues <- colorRampPalette(c("darkblue","lightblue"))
grays <- colorRampPalette(c("black","lightgray"))

ROGBP <- colorRampPalette(c("red","orange","green","blue","purple"))
# Makes an ROGBP function with an alpha channel
ROGBP_alpha <- function(alpha){
  x <- colorRampPalette(c(
    rgb(1,0,0,alpha), # red
    rgb(1,0.5,0.25,alpha), # orange
    rgb(0,1,0,alpha), # green 
    rgb(0,0,1,alpha), # blue
    rgb(0.5,0,0.5,alpha)), # purple
    alpha=TRUE)
  return(x)
}

@@

YieldLT <- function(...,Ref=1,Yrs=-10){Yield(...,Ref=Ref,Yrs=Yrs)}

@@

plot_MSE_ts <- function(
myvarName="SSB",
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = median,
scenNames,
OMNames,
MPNamesSub = NULL,
MPNamesSub_legtext=MPNamesSub,
MPNamesRef = NULL, # Name of reference MP
FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
legtext_o = NULL, # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,
sims = NULL, # which simulation runs should be used to generate the plot when plot_type="sims"?
plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
                   # "tradeoff" plots tradeoff plots by MP
                   # "addind" plot additional indices from AddInd
                   # "sims" plot time series for individual sim runs
proyear_phase=NULL,
proyear_phase_FUNName="median",
PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
PMy = P100, # Performance metric function y (y-axis) for tradeoff plots)
PMx_Yrs=-10, # Defaults to the last 10 years 
PMy_Yrs=-10, # Defaults to the last 10 years
mar=c(1,1,1,1),
oma=c(6,4,3,3),
mgp=c(1.5,0.2,0),
cex.axis=1.2,
plot_format="landscape", # "portrait" or "landscape". Are species plots next to each other or stacked vertically?
cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
xlabel = "Management year",
main_line = 1, # Line for main column labels
xlim = NULL,
ylim = NULL,
assessmentYears=NULL,
assessmentYears_MP="SCA_10",
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.5),
legend_x.intersp = 1,
legend_xjust=0,
legend_ncol=1,
legend_horiz=TRUE,
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=NULL, # values to pass into abline(h=hline)
vline=NULL, # values to pass into abline(v=vline)
hline_lty=3,
vline_lty=3,
...
){
if(is.null(legtext_o)){
  legtext_o <- seq_along(MPNamesSub)
}

@@

if(plot_type=="addind"){plot_format <- "portrait"}
if(plot_format=="landscape"){
  mfcol <- c(dim1,dim2)}else{
  mfcol <- c(dim2,dim1)
  }

par(mfcol=mfcol,mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="r",yaxs="r",cex.axis=cex.axis)

topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
bottomPanels <- length(scenNames)*seq_along(OMNames)
leftPanels <- seq_along(scenNames)
rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))
if(is.null(legend_panel)){
legend_panel <- bottomPanels[1]
}

### LOOP THROUGH MSE OBJECTS
for(outName_i in MSEoutNames){

@@

matplot(projYears_i#as.numeric(rownames(myvarsubStat))
        ,myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="",...)
#title(main=colLabsAll[i],line=1)

grid(nx=NA,ny=NULL)
if(is.null(assessmentYears)){
assessmentYears_i <- apply(do.call(cbind,lapply(out_i@PPD[[assessmentYears_MP]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
}else{
assessmentYears_i <- assessmentYears  
}
abline(v=assessmentYears_i,lty="1111",lwd=2)
}
    if(plot_type=="sims"){
      cols <-  ROGBP(length(sims))
      ltys <-  1:length(MPNamesSub)
      pchs <-  NA
      lwds <-  3
      types <- "l"

@@

      for(MP_j in MPNamesSub){
      j <- match(MP_j,MPNamesSub)
      myvarsub_j <- myvarsub[,j,]
      lty <- ltys[j]
      if(j==1){
      matplot(projYears_i,
              t(myvarsub_j), 
              col=cols,lty=lty,lwd=lwds,type=types,
              xaxt=xaxt_i,yaxt=yaxt_i,
              xlim=xlim,ylim=ylim,xlab="",ylab="",...)
      #title(main=colLabsAll[i],line=1)

      grid(nx=NA,ny=NULL)
      abline(v=assessmentYears_i,lty=2,lwd=1)
      }else{
        matpoints(t(myvarsub_j), 
                col=cols,lty=lty,lwd=lwds,type=types
                )        
      }
    }
    }

if(plot_type=="addind"){
  PPDYears_i <- local({
    a <- c(histYears,projYears_i)
    a[-length(a)]
  })
if(is.null(assessmentYears)){
assessmentYears_i <- apply(do.call(cbind,lapply(out_i@PPD[[MPNamesSub]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
}else{
  assessmentYears_i <- assessmentYears
}

@@

plot_boot_vec(myvarsub[,j,],
              col_lines = col_AddInd[j],
              add=ifelse(j!=1,TRUE,FALSE),
              xlim=xlim,ylim=ylim,...)

}
grid(nx=NA,ny=NULL)
abline(v=assessmentYears_i,lty=2,lwd=1)
}

@@

if(is.null(proyear_phase)){
  proyear_phase <- out_i@proyears
}
proyear_phase_FUN <- get(proyear_phase_FUNName)
Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase,drop=FALSE] %>% apply(1:2,proyear_phase_FUN)
Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase,drop=FALSE] %>% apply(1:2,proyear_phase_FUN)

matplot(Fstatus,Bstatus,
        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlab="",ylab="",xlim=xlim,ylim=ylim,
        ...
        )
points(apply(Fstatus,2,proyear_phase_FUN),
       apply(Bstatus,2,proyear_phase_FUN),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))

@@

if(i%in%topPanels&i%in%leftPanels){
  if(length(proyear_phase)>1){
    leg_text_phase <- paste0(proyear_phase_FUNName,"(proyears ",paste(range(proyear_phase),collapse="-"),")")
  }else{
    leg_text_phase <- paste0("proyear ",proyear_phase)
  }
  legend("topright",legend=leg_text_phase,bty="n",text.col="black",text.font = 2,x.intersp = legend_x.intersp)
}

@@

if(i%in%rightPanels){
row.ct <- which(rightPanels==i)
rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2
text(x=par("usr")[2]+diff(par("usr")[1:2])*0.1
     ,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=1)
}

@@

if(i==legend_panel&plot_type%in%c("huynh","phase","tradeoff")){
   legend(legend_x,
          inset=legend_inset,
       horiz=legend_horiz,bty="n",
       legend=MPNamesSub_legtext[legtext_o],
       col=makeOpaque(cols)[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],pch=pchs[legtext_o],
       cex=legend_cex,
       xpd=NA,
       x.intersp = legend_x.intersp,
       xjust=legend_xjust,
       ncol=legend_ncol
       )

@@

if(textlabpos[i]=="lo"){text(x=x,y=rep(par("usr")[3]),labels=Statmedtext,srt=90,adj=c(-0.1,0.5),font=1)}
if(textlabpos[i]=="up"){text(x=x,y=rep(par("usr")[4]),labels=Statmedtext,srt=90,adj=c(1.2,0.5),font=1)}

@@

text(x=par("usr")[2]*1.05,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=1)
}

@@

```{r function PMsummary}

# compute and plot summary statistics for Performance metrics
PMsummary <- function(PMName,
                      OMNames = OMNames_user,
                      scenNames,
                      MPs = NULL,
                      xaxis_label = NULL,
                      xaxis_label_outer = "Management procedure",
                      slot_to_plot = "Prob", # Can be either "Prob" or "Stat"
                      main_line = -1.5,
                      hline = NULL,
                      hline_lty = 3,
                      par_args = list(mfrow = c(length(OMNames),1), mar = c(0,2,0,1), 
                                      oma = c(3,3,1,0), mgp = c(0.8,0.2,0), tck = -0.01, cex.axis=1.0),
                      y.cex.axis=1.2,
                      n_yr_groups = 1, # Number of groups to split years into
                      group_space = NULL,  # Additional spacing between groups of boxes
                      ...){
  PM <- get(PMName)
  dots <- list(...)
  if(!"ylab"%in%names(dots)){
    dots$ylab <- PMName
  }
  if(!"col"%in%names(dots)){
    colorFUN = colorRampPalette(c("lightblue","darkblue"))
    dots$col <-  colorFUN(n_yr_groups)
  }
  if(!"outcol"%in%names(dots)){
    dots$outcol <- dots$col
  }
  if(!"outpch"%in%names(dots)){
    dots$outpch <- 16
  }
  if(is.null(group_space)){
    group_space <- (n_yr_groups-1)*.75
  }

@@

  for (OMNames_i in OMNames){
    Names_i <- gsub("^OM_","",OMNames_i)
    MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                           "_",
                           rep(scenNames,length(OMNames_i))
    )
    out_list_i <- list()
    for(MSEoutNames_ij in MSEoutNames_i){
      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
      MSEout_ij <- get(MSEoutNames_ij)
      proyears_ij <- MSEout_ij@proyears
      yr_ij <- 1:proyears_ij
      breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))

      yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))

      for(k in 1:n_yr_groups){
        MSEoutNames_ijk <- paste(MSEoutNames_ij,sprintf("%02.0f",k),sep="_")  
        PMout_ijk <- PM(MSEout_ij,Yrs=range(yr_ij[yr_groups_ij==k]))
        MPs_ijk <- PMout_ijk@MPs
        out_ijk <- slot(PMout_ijk,slot_to_plot)
        if(!is.null(MPs)){ # Possibly subset MPs
          out_ijk <- out_ijk[,match(MPs,MPs_ijk)]
          MPs_ijk <- MPs
        }
        dimnames(out_ijk) <- list("sim"=1:dim(out_ijk)[1], "MPs"=MPs_ijk)
        out_ijk <- cbind("scen"=scenNames_j,"yr_group"=k,as.data.frame(out_ijk))
        out_list_i[[MSEoutNames_ijk]] <- out_ijk

      } # end n_yr_groups
    } 
    # Combine scenario outputs into large data frame with scen column indicating scenario
    out_df_i <- do.call(rbind,out_list_i)
    out_df_i <- reshape2::melt(data=out_df_i,id.vars=c("scen","yr_group"))
    out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i

    # Plot stuff
    dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
    n_group <- length(unique(out_df_i$yr_group))
    n_variable <- length(unique(out_df_i$variable))

    group_space_add <- rep(1:n_variable,each=n_group)*group_space
    box_at <- 1:(n_group*n_variable)+group_space_add

    dots$cex.axis <- y.cex.axis

    do.call(boxplot,c(list(formula = value ~ yr_group + variable, data = out_df_i,
                           main = "", at = box_at),dots))

    mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)

    if(!is.null(hline)){
      abline(h=hline,lty=hline_lty)
    }
  }
  if(is.null(xaxis_label)){xaxis_label <- MPs}
  xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=length(xaxis_label)),2,mean)

  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=1)

@@

```{r data}
# Read in list of rdat modifications used when plotting bam results compared with Hist objects
load("rdatmods.RData")

# Read in data for original operating models
for(file.i in list.files("OM")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM",file.i)))
}

# Read in data for modified operating models
file_OMNames_base <- list.files("OM_modified")[grepl("base.rds$",list.files("OM_modified"))]
OMNames_base <- gsub(".rds$","",file_OMNames_base)
for(file.i in file_OMNames_base){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
}

@@

```{r boxplots plots combining multiple scenarios, eval=TRUE}
# Summary plots combining all years and all scenarios
for(i in match(sN_plot,sN_all)){
